A Structural and Functional Bioinformatics Study of QTY-designed Retinylidene Proteins

### 2025-05-02 Paper/Source/manuscript.tex
Write supplementary material
cancel line numbering and prepare to convert to word

\documentclass[fleqn,10pt,lineno]{manuscript}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul, hyperref}
\usepackage[utf8]{inputenc}

@@

\subsection*{The QTY code}

@@

@@

* Future scopes and potential applications.

@@

* Conclusion

@@

Regarding QTY-designed OPN2, the system was constructed directly using GROMACS. The protein was centered in a rectangular box with dimensions equivalent to those of native OPN2. The equilibration involved a sequence of simulations: a 250-ps NVT equilibration, followed by 125-ps and 1500-ps NPT equilibrations, totaling an equilibration duration that matches that of the natural OPN2. All other configurations and parameters are identical to those of the original OPN2.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
	\caption{Protein sequence alignments}
	\label{fig:sequences}
\end{figure}

>>>>

\documentclass[fleqn,10pt]{manuscript}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul, hyperref}
\usepackage[utf8]{inputenc}

@@

\subsection*{The rationale of the QTY code}

@@

MD Results

* different states - binding pocket residues + ligand orientation

* bond length, angle, dihedral, non-bonded interaction lengths graph

* by-helix rmsd

* by-residue IE

* hbond

* overall rmsd, gyrate, rmsf, IE

@@

Future scopes and potential applications.

@@

Conclusion

@@

Regarding QTY-designed OPN2, the system was constructed directly using GROMACS. The protein was centered in a rectangular box with dimensions equal to those of native OPN2. The equilibration involved a sequence of simulations: one 250-ps NVT equilibration, followed by one 125-ps and one 1500-ps NPT equilibrations, totaling an equilibration duration that matches that of the natural OPN2. All other configurations and parameters are identical to those of the original OPN2.

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/sequences.jpg}
	\caption{Protein sequence alignments --- THIS FIGURE NEEDS REVISION!!!!!}
	\label{fig:sequences}
\end{figure}
